AP/PA Tables ITHIM Global

### 2023-08-23 summary_tables_PA_AP.Rmd
updated documentation
updated how the reference scenario is used

# function to convert scenario names
get_qualified_scen_name <- function(cs){
  qualified_scen_name <- ""
  if (cs == 'base')
    qualified_scen_name <- 'Baseline'
  else if(cs == "sc_walk")
    qualified_scen_name <- 'Walking'
  else if(cs == "sc_cycle")
    qualified_scen_name <- 'Bicycling'
  else if(cs == "sc_car")
    qualified_scen_name <- 'Car'
  else if(cs == "sc_motorcycle")
    qualified_scen_name <- 'Motorcycling'
  else if(cs == "sc_bus")
    qualified_scen_name <- 'Public Transport'

@@

# scenario definition
scenario_name <- io[[city]]$ithim_run$scenarios_used
reference_scenario <- io[[city]]$ithim_run$reference_scenario

@@

@@

  # add scenario specific PM2.5 concentration levels and the change in PM2.5 compared to the baseline
  summary$scenario_PM <- round(io[[cities[x]]]$outcomes$scenario_pm, digits=2)
  summary$change_PM <- round(io[[cities[x]]]$outcomes$scenario_pm - io[[cities[x]]]$outcomes$scenario_pm[1], digits=2)
  names(summary)[1] <- "Scenario"

@@

# Average physical activity levels (MMETs) in each city

@@

  # calculate difference to baseline scenario
  summary2$change_PM <- round(io[[cities[x]]]$outcomes$scenario_pm - io[[cities[x]]]$outcomes$scenario_pm[1], digits = 2)
  names(summary2)[1] <- "Scenario"

@@

  cat("\n \n")
  cat( paste('#### Summary statistics of individual level PM2.5 exposure levels and total transport related CO2 emissions\n' ))
  l[[cities[x]]] <- left_join(summary2, td, by = "Scenario")
  l[[cities[x]]]$city <- cities[x]
  print(kable(cbind(summary2, td), caption = cities[x]))

>>>>

# function to convert scenario names
get_qualified_scen_name <- function(cs){
  qualified_scen_name <- ""
  if (cs == 'base' | cs == 'Baseline' | cs == 'baseline')
    qualified_scen_name <- 'Baseline'
  else if(cs == "sc_walk")
    qualified_scen_name <- 'Walking'
  else if(cs == "sc_cycle")
    qualified_scen_name <- 'Bicycling'
  else if(cs == "sc_car")
    qualified_scen_name <- 'Car'
  else if(cs == "sc_motorcycle")
    qualified_scen_name <- 'Motorcycling'
  else if(cs == "sc_bus")
    qualified_scen_name <- 'Public Transport'

@@

# scenario definition
scenario_name <- io[[city]]$ithim_run$scenarios_used
ref_scen <- io[[cities[1]]]$ithim_run$reference_scenario
reference_scenario <- get_qualified_scen_name(ref_scen)

@@

cat(paste0('The change in PM2.5 levels is given as the difference to the reference scenario: ', reference_scenario))

@@

  # add scenario specific PM2.5 concentration levels and the change in PM2.5 compared to the baseline
  summary$scenario_PM <- round(io[[cities[x]]]$outcomes$scenario_pm, digits=2)

  # find location of reference scenario in vector of all scenarios
  loc_ref <- which(new_scen_names == reference_scenario)

  # calculate the PM2.5 changes between the reference scenario and the other scenarios
  summary$change_PM <- round(io[[cities[x]]]$outcomes$scenario_pm - io[[cities[x]]]$outcomes$scenario_pm[loc_ref], digits=2)
  names(summary)[1] <- "Scenario"

@@

# Average baseline physical activity levels (MMETs) in each city

@@

  # calculate difference to reference scenario
  summary2$change_PM <- round(io[[cities[x]]]$outcomes$scenario_pm - io[[cities[x]]]$outcomes$scenario_pm[loc_ref], digits = 2)
  names(summary2)[1] <- "Scenario"

@@

  cat("\n \n")
  cat( paste('#### Summary statistics of individual level PM2.5 exposure levels and total transport related CO2 emissions\n' ))
  cat(paste0('The change in PM2.5 levels is given as the difference to the reference scenario: ', reference_scenario))
  l[[cities[x]]] <- left_join(summary2, td, by = "Scenario")
  l[[cities[x]]]$city <- cities[x]
  print(kable(cbind(summary2, td), caption = cities[x]))
